Pattern matching for\\ $(231,213)$-avoiding permutations

### 2015-02-02 article.tex
modification : used of [] for an element of a permutation instead of ()

\begin{corollary}
Let $\pi \in \AV_n(213,231)$. We have
$$
\stripe{\pi}{i} =
\begin{cases}
			\ustep & \text{if $\pi(i)$ is the minimal element of $\pi[i:]$}\\    
			\dstep & \text{if $\pi(i)$ is the maximal element of $\pi[i:]$}\\
	\end{cases}
	$$
\end{corollary}

@@

			\begin{proof}
			Given a ascent (descent) segment $S(s)$,
			if we want to
			match the suffix $s_ns_{s-1}...s_1$
			starting with an ascent (descent),
			and given that we know every
			match of $s_{s-1}...s_1$,
			the optimal way of matching
			$s_{s-1}...s_1$
			is to choose the match
			that minimize (maximize)
			the maximal (minimal)
			element of the match
			and that allow a match
			of $s_n$.			
			In other word if we want to match 
			$\pmotif[IMP(s):]$
			with $\ptext[i:]$
			and match $IMP(s)$
			with $i$.
			The optimal way
			of matching
			$\pmotif[IMP(s-1):]$
			is to choose the
			minimal (maximal) element $\ptext(i')$
			such that :
			(1) $\pmotif[IMP(s-1):]$ is matched with $\ptext[i':]$
			and $IMP(s-1)$ is matched with $e$.
			(2) The segment $S(s)$ is matched with $\ptext[i:i'-1]$
			and $IMP(s)$ is matched with $i$.
			(3) Every elements of the match of (2),
			is inferior (superior) to the minimal (maximal) element of the match of (1).
			Indeed when we will 
			match $s_{n+1}s_ns_{s-1}...s_1$
			more element will be available,
			because every matched 
			element of $s_{n+1}$
			must be superior (inferior)
			to every matched element
			of $s_{s-1}...s_1$.\\

@@

						MIN_{i<i'}\{0\} \cup \{i' |\text{ $i'$ such that } & 
						\text{if $\stripe{\pmotif}{IMP(1)}=\ustep$}
						\\
						\text{ $LIS(i,i',\ptext(i')) \leq S(1)$}\}&\\

@@

						MAX_{i<i'}\{0\} \cup \{i' |\text{ $i'$ such that } &
						\text{if $\stripe{\pmotif}{IMP(1)}=\dstep$} \\
						\text{ $LDS(i,i',\ptext(i')) \leq S(1)$}\}&\\

@@

			if $|\pmotif| \notin  \x : $\\		
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $min<\ptext(j)<max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|+1,j)= true $\\

			if $|\pmotif| \in  \x : $\\		
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,|\ptext|)= \left\{ 
					\begin{array}{l l}
						true & \text{if $min<\ptext(|\ptext|)<max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|+1,|\ptext|)= true $\\

			if $|\pmotif| \notin  \x$  
			and $|\pmotif| \in  \y$ 
			and $\pmotif(|\pmotif|)$ is the maximal element: \\		
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $min<\ptext(j)<max$
						}\\
						&\text{$\ptext(j)$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|+1,j)= true $\\

			if $|\pmotif| \in  \x$  
			and $|\pmotif| \in  \y$ 
			and $\pmotif(|\pmotif|)$ is the maximal element: \\		
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,|\ptext|)= \left\{ 
					\begin{array}{l l}
						true & \text{if $min<\ptext(|\ptext|)<max$
						}\\
						&\text{$\ptext(|\ptext|)$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|+1,|\ptext|)= true $\\

@@

						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,\ptext(j),max}(i+1,k) 
							& \text{if $\stripe{\pmotif}{i}=\ustep$
							and $i \notin \x$}\\
							& \text{and $i \notin \y$ }\\
							& \text{and $min<\ptext(j)<max$} \\
						&\\

						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,min,\ptext(j)}(i+1,k) 
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							& \text{and $i \notin \x$ and $i \notin \y$  }\\
							& \text{and $min<\ptext(j)<max$} \\		
						&\\

						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,j+1) 
							& \text{if $\stripe{\pmotif}{i}=\ustep$}\\
							& \text{and $i \in \x$ and $i \notin \y$}\\
							& \text{and $min<\ptext(j)<max$} \\
						&\\

						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,j+1) 
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							& \text{and $i \in \x$ and $i \notin \y$ }\\
							& \text{and $min<\ptext(j)<max$} \\

@@

						\mathbb{P}_{\bmotif,\ptext,\ptext(j),max}(i+1,\ptext^{-1}(\ptext(j)+1)) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \notin \x$ and $i \in \y$}\\
							& \text{and $min<\ptext(j)<max$} \\
							&\text{and $\ptext^{-1}(\ptext(j)+1)>j$}\\
						&\\

						\mathbb{P}_{\bmotif,\ptext,min,\ptext(j)}(i+1,\ptext^{-1}(\ptext(j)-1)) 
							&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
							&\text{and $i \notin \x$ and $i \in \y$ }\\	
							& \text{and $min<\ptext(j)<max$} \\
							&\text{and $\ptext^{-1}(\ptext(j)-1)>j$}\\
						&\\

						\mathbb{P}_{\bmotif,\ptext,\ptext(j)),max}(i+1,j+1) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \in \x$ and $i \in \y$}\\ 
							&\text{and $\ptext(j)+1=\ptext(j+1)$ }\\
							& \text{and $min<\ptext(j)<max$} \\
						&\\

						\mathbb{P}_{\bmotif,\ptext,min,\ptext(j)}(i+1,j+1)
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							&\text{and $i \in \x$ and $i \in \y$}\\ 
							&\text{and $\ptext(j)-1=\ptext(j+1)$ }\\
							& \text{and $min<\ptext(j)<max$} \\
						&\\	
						False & Otherwise\\																		
					\end{array} \right. $\\

@@

			At each step (i,j),
			If $i \notin \x$ and $i \notin \y$,
			we match the current element of $\pmotif$ ($\pmotif(i)$)
			with the current element of $\ptext$ ($\ptext(j)$), if possible.
			Then we match $\pmotif[i+1:]$ with 
			every suffixes $\ptext$ starting after $j$.\\

			If $i \in \x$ and $i \notin \y$,
			we match $\pmotif(i)$ to $\ptext(j)$, 
			then we match $\pmotif[i+1:]$ with $\ptext[j+1:]$
			with the condition that
			$\pmotif(i+1)$ is matched to $\ptext(j+1)$.\\

			If $i \notin \x$, $i \in \y$ and i is a descent,
			we match $\pmotif(i)$ to $\ptext(j)$, 
			then we match $\pmotif[i+1:]$ 
			with $\ptext[\ptext^{-1}(\ptext(j)-1):]$
			with the condition that
			$\pmotif(i+1)$ is matched to the element $\ptext(j)-1$.\\

			If $i \notin \x$, $i \in \y$ and i is an ascent,
			we match $\pmotif(i)$ to $\ptext(j)$, 
			then we match $\pmotif[i+1:]$ 
			with $\ptext[\ptext^{-1}(\ptext(j)+1):]$
			with the condition that
			$\pmotif(i+1)$ is matched to the element $\ptext(j)+1$.\\

			If $i \in \x$, $i \in \y$ and i is a descent,
			we match $\pmotif(i)$ to $\ptext(j)$, 
			then we match $\pmotif[i+1:]$ with $\ptext[j+1:]$
			with the condition that
			$\pmotif(i+1)$ is matched to $\ptext(j+1)$,
			and that $\ptext(j+1)=\pmotif(i)-1$.\\

			If $i \in \x$, $i \in \y$ and i is an ascent,
			we match $\pmotif(i)$ to $\ptext(j)$, 
			then we match $\pmotif[i+1:]$ with $\ptext[j+1:]$
			with the condition that
			$\pmotif(i+1)$ is matched to $\ptext(j+1)$,
			and that $\ptext(j+1)=\pmotif(i)+1$.\\

>>>>

\begin{corollary}
Let $\pi \in \AV_n(213,231)$. We have
$$
\stripe{\pi}{i} =
\begin{cases}
			\ustep & \text{if $\pi[i]$ is the minimal element of $\pi[i:]$}\\    
			\dstep & \text{if $\pi[i]$ is the maximal element of $\pi[i:]$}\\
	\end{cases}
	$$
\end{corollary}

@@

			\begin{proof}
			Given a ascent (descent) segment $S(s)$,
			if we want to
			match the suffix $s_ns_{s-1}...s_1$
			starting with an ascent (descent),
			and given that we know every
			match of $s_{s-1}...s_1$,
			the optimal way of matching
			$s_{s-1}...s_1$
			is to choose the match
			that minimize (maximize)
			the maximal (minimal)
			element of the match
			and that allow a match
			of $s_n$.			
			In other word if we want to match 
			$\pmotif[IMP(s):]$
			with $\ptext[i:]$
			and match $IMP(s)$
			with $i$.
			The optimal way
			of matching
			$\pmotif[IMP(s-1):]$
			is to choose the
			minimal (maximal) element $\ptext[i']$
			such that :
			(1) $\pmotif[IMP(s-1):]$ is matched with $\ptext[i':]$
			and $IMP(s-1)$ is matched with $e$.
			(2) The segment $S(s)$ is matched with $\ptext[i:i'-1]$
			and $IMP(s)$ is matched with $i$.
			(3) Every elements of the match of (2),
			is inferior (superior) to the minimal (maximal) element of the match of (1).
			Indeed when we will 
			match $s_{n+1}s_ns_{s-1}...s_1$
			more element will be available,
			because every matched 
			element of $s_{n+1}$
			must be superior (inferior)
			to every matched element
			of $s_{s-1}...s_1$.\\

@@

						MIN_{i<i'}\{0\} \cup \{i' |\text{ $i'$ such that } & 
						\text{if $\stripe{\pmotif}{IMP(1)}=\ustep$}
						\\
						\text{ $LIS(i,i',\ptext[i']) \leq S(1)$}\}&\\

@@

						MAX_{i<i'}\{0\} \cup \{i' |\text{ $i'$ such that } &
						\text{if $\stripe{\pmotif}{IMP(1)}=\dstep$} \\
						\text{ $LDS(i,i',\ptext[i']) \leq S(1)$}\}&\\

@@

			if $|\pmotif| \notin  \x : $\\		
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $min<\ptext[j]<max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|+1,j)= true $\\

			if $|\pmotif| \in  \x : $\\		
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,|\ptext|)= \left\{ 
					\begin{array}{l l}
						true & \text{if $min<\ptext[|\ptext|]<max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|+1,|\ptext|)= true $\\

			if $|\pmotif| \notin  \x$  
			and $|\pmotif| \in  \y$ 
			and $\pmotif[|\pmotif|]$ is the maximal element: \\		
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $min<\ptext[j]<max$
						}\\
						&\text{$\ptext[j]$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|+1,j)= true $\\

			if $|\pmotif| \in  \x$  
			and $|\pmotif| \in  \y$ 
			and $\pmotif[|\pmotif|]$ is the maximal element: \\		
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|,|\ptext|)= \left\{ 
					\begin{array}{l l}
						true & \text{if $min<\ptext[|\ptext|]<max$
						}\\
						&\text{$\ptext[|\ptext|]$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,min,max}(|\pmotif|+1,|\ptext|)= true $\\

@@

						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,\ptext[j],max}(i+1,k) 
							& \text{if $\stripe{\pmotif}{i}=\ustep$
							and $i \notin \x$}\\
							& \text{and $i \notin \y$ }\\
							& \text{and $min<\ptext[j]<max$} \\
						&\\

						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,min,\ptext[j]}(i+1,k) 
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							& \text{and $i \notin \x$ and $i \notin \y$  }\\
							& \text{and $min<\ptext[j]<max$} \\		
						&\\

						\mathbb{P}_{\bmotif,\ptext,t(j),max}(i+1,j+1) 
							& \text{if $\stripe{\pmotif}{i}=\ustep$}\\
							& \text{and $i \in \x$ and $i \notin \y$}\\
							& \text{and $min<\ptext[j]<max$} \\
						&\\

						\mathbb{P}_{\bmotif,\ptext,min,t(j)}(i+1,j+1) 
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							& \text{and $i \in \x$ and $i \notin \y$ }\\
							& \text{and $min<\ptext[j]<max$} \\

@@

						\mathbb{P}_{\bmotif,\ptext,\ptext[j],max}(i+1,\ptext^{-1}(\ptext[j]+1)) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \notin \x$ and $i \in \y$}\\
							& \text{and $min<\ptext[j]<max$} \\
							&\text{and $\ptext^{-1}(\ptext[j]+1)>j$}\\
						&\\

						\mathbb{P}_{\bmotif,\ptext,min,\ptext[j]}(i+1,\ptext^{-1}(\ptext[j]-1)) 
							&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
							&\text{and $i \notin \x$ and $i \in \y$ }\\	
							& \text{and $min<\ptext[j]<max$} \\
							&\text{and $\ptext^{-1}(\ptext[j]-1)>j$}\\
						&\\

						\mathbb{P}_{\bmotif,\ptext,\ptext[j]),max}(i+1,j+1) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \in \x$ and $i \in \y$}\\ 
							&\text{and $\ptext[j]+1=\ptext[j+1]$ }\\
							& \text{and $min<\ptext[j]<max$} \\
						&\\

						\mathbb{P}_{\bmotif,\ptext,min,\ptext[j]}(i+1,j+1)
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							&\text{and $i \in \x$ and $i \in \y$}\\ 
							&\text{and $\ptext[j]-1=\ptext[j+1]$ }\\
							& \text{and $min<\ptext[j]<max$} \\
						&\\	
						False & Otherwise\\																		
					\end{array} \right. $\\

@@

			At each step (i,j),
			If $i \notin \x$ and $i \notin \y$,
			we match the current element of $\pmotif$ ($\pmotif[i]$)
			with the current element of $\ptext$ ($\ptext[j]$), if possible.
			Then we match $\pmotif[i+1:]$ with 
			every suffixes $\ptext$ starting after $j$.\\

			If $i \in \x$ and $i \notin \y$,
			we match $\pmotif[i]$ to $\ptext[j]$, 
			then we match $\pmotif[i+1:]$ with $\ptext[j+1:]$
			with the condition that
			$\pmotif[i+1]$ is matched to $\ptext[j+1]$.\\

			If $i \notin \x$, $i \in \y$ and i is a descent,
			we match $\pmotif[i]$ to $\ptext[j]$, 
			then we match $\pmotif[i+1:]$ 
			with $\ptext[\ptext^{-1}(\ptext[j]-1):]$
			with the condition that
			$\pmotif[i+1]$ is matched to the element $\ptext[j]-1$.\\

			If $i \notin \x$, $i \in \y$ and i is an ascent,
			we match $\pmotif[i]$ to $\ptext[j]$, 
			then we match $\pmotif[i+1:]$ 
			with $\ptext[\ptext^{-1}(\ptext[j]+1):]$
			with the condition that
			$\pmotif[i+1]$ is matched to the element $\ptext[j]+1$.\\

			If $i \in \x$, $i \in \y$ and i is a descent,
			we match $\pmotif[i]$ to $\ptext[j]$, 
			then we match $\pmotif[i+1:]$ with $\ptext[j+1:]$
			with the condition that
			$\pmotif[i+1]$ is matched to $\ptext[j+1]$,
			and that $\ptext[j+1]=\pmotif[i]-1$.\\

			If $i \in \x$, $i \in \y$ and i is an ascent,
			we match $\pmotif[i]$ to $\ptext[j]$, 
			then we match $\pmotif[i+1:]$ with $\ptext[j+1:]$
			with the condition that
			$\pmotif[i+1]$ is matched to $\ptext[j+1]$,
			and that $\ptext[j+1]=\pmotif[i]+1$.\\
